Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-26 doc/manuscript/manuscript.Rmd
Add more text to manuscript discussion

Our network-based approach to correlating MLGs with MCGs revealed a large and complex network (Fig. \@ref(biggraph)). 
Community analysis showed 51 communities, 15 of which consisted of a single MLG unconnected with any other community indicating that just 9.09% of the 165 MLGs are unable to cross with any other MLG in this data set.
The three communities with the most members contained 8 of the ten most abundant MCGs. 
Comparing these communities with Bruvo's genetic distance revealed and average distance of 0.451 among communities and an average distance of 0.437 within communities, showing no significant difference.
Overall, there was no clear pattern to the association between MLG and MCGs.

@@

Of particular interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as an indicator for clonal lineages [@otto-hanson2011variation; @kohn1995clonal; @lehner2015analysis]. 
As genetic markers became more widely available, studies began to find conflicting results regarding the association between MCG and MLG [@sirjusingh2001characterisation; @lehner2015analysis].

>>>>

Our network-based approach to correlating MLGs with MCGs revealed a large and complex network (Fig. \@ref(biggraph)). 
Community analysis showed 51 communities, 15 of which consisted of a single MLG unconnected with any other community indicating that just 9.09% of the 165 MLGs are unable to cross with any other MLG in this data set.
Of all the MLGs, MLG 25 had 57 neighbors that shared the same mycelial compatibility group. 
The three communities with the most members contained 8 of the ten most abundant MCGs. 
Comparing these communities with Bruvo's genetic distance revealed and average distance of 0.451 among communities and an average distance of 0.437 within communities, showing no significant difference.
Overall, there was no clear pattern to the association between MLG and MCGs.

@@

Of particular interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@otto-hanson2011variation; @kohn1995clonal; @carbone1999patterns; @lehner2015analysis]. 
When using genetic markers with MCGs, there are three basic relationship patterns, 1) One MLG to one MCG, 2) Several MLGs belong to one MCG, and 3) Several MCGs belong to one MLG, noting that 2 and 3 are not mutually exclusive.
Our results show all three (Fig. \@ref(biggraph)) where only 12 of the observed MLGs and MCGs fit into the first pattern.

All three of these patterns have been observed together in separate studies [@aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic].
